Weather Data Integration and Assimilation System\\

### 2020-02-09 thesis.tex
It could have been much more easier to modify and compile thesis if each chapter was on a separate file. Page nos should be Roman numerals until Chap 1 beings.
Moved Other Lit Review Sys to diff file

\dbc{It could have been much more easier to modify and compile thesis if each chapter was on a separate file. Page nos should be Roman numerals until Chap 1 beings.}

...
\dbc{Start the para with a couple of sentences/para on weather prediction and NWMs. In another para mention about CUrW and its need to integrate and share data. Give citations of 1-2 good introductory sources on NWMs and another citation to CUrW website.}

@@

\section{Data Integration and Assimilation Systems}
\label{se:dias}

\section{Meteorological Assimilation Data Ingest System}
\label{se:madis}

\section{Summary}

>>>>

@@

\import{lit/}{sec_3-other-systems.tex}
